Supplementary Materials

### 2023-06-30 manuscript/manuscript.tex
supp, methods

We tested multiple different optimization routines, finding that BOBYQA
outperformed alternatives \parencite{Powell_undated-ec}. We inspected and
confirmed convergence with diagnostic plots finding stable optima across 10,000
random starts (see Supplementary Materials Section XXX).

>>>>

We tested multiple different optimization routines, finding that BOBYQA
outperformed alternatives \parencite{Powell_undated-ec}. We inspected and
confirmed convergence with diagnostic plots finding stable optima across 10,000
random starts (see Supplementary Materials Section \ref{suppsec:optima}).

### 2023-06-30 manuscript/supplementary.tex
supp, methods

\subsection{Optimization Diagnostics}

\begin{figure}[!htb]
  \label{suppfig:diag-plot}
  \centering
  \includegraphics[width=\textwidth]{figures/supplementary/figure_feature_priority_yri_full_diag.pdf}
  \caption{
      An optimization diagnostic plot showing the }
\end{figure}

\subsection{Chromosome Fit Figures}
\clearpage

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{figures/supplementary/pred_plot_chr6.pdf}
  \label{suppfig:fit-chr6}
\end{figure}

>>>>

\subsection{Optimization Diagnostics}
\label{suppsec:optim}

We only show one optimization diagnostic plot here (Supplementary Figure
\ref{suppfig:diag-plot}), but the can be easily calculated from the model
pickle files in the XXX repository (XXX). In one case, our optimization
diagnostics indicated that the best optima across 10,000 random starts was one
of few of the top 100 hits that were hitting either an alternate likelihood
mode, or the optimization routine had numeric issues. In this one case, we
removed the top hit and used the second, which was the consensus among the
other top 100 optima.

\begin{figure}[htbp]
  \label{suppfig:diag-plot}
  \centering
  \includegraphics[width=\textwidth]{figures/supplementary/figure_feature_priority_yri_full_diag.pdf}

  \caption{ An optimization diagnostic plot showing the 100 top optima. Heatmap
  colors indicate probability mass for the DFE parameters (top four rows).
Estimates of $\pi_0$ and $\mu$ are shown in the bottom two rows. This is the
optimization plot for YRI Feature Priority model.}

\end{figure}
\clearpage

\subsection{Chromosome Fit Figures}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{figures/supplementary/pred_plot_chr6.pdf}
  \caption{Note: we mask the MHC region during model fit.}
  \label{suppfig:fit-chr6}
\end{figure}
